Local real space operators for translating Stokes Q/U to E/B maps on the sphere

### 2017-10-09 article/sections/appendix.tex
completed first pass at the multupole filtering section
made some refinements to Sections 1 and 2 of the paper

>>>>

\subsection{Local convolution kernels using standing Healpix routines}\label{sec:rot_ker_healpix}
Healpix uses Euler angles given in the z-y-z convention in contrast to the Euler angle definitions given in \sec{sec:euler} which are in z-y1-z2 convention. The two set of Euler angles are related by the following relations $(\alpha,\beta,\gamma)_{\rm z-y-z} = (\gamma,\beta,\alpha)_{\rm z-y1-z2}$ \cite{varshalovich}. We know the exact form of the harmonic coefficients for the kernels when they are centered around the north pole. Therefore the kernels centered around any arbitrary Healpix pixel $\hat{n}_i$ can be calculated by simply rotating these harmonic coefficients by the Euler angles $(0,\theta_i,\phi_i)_{\rm z-y-z}$ and synthesizing the kernel by evaluating the harmonic sum.
\subsection{The correlation function and radial cut offs.}\label{sec:corrfn_rad_cutoff}
